---
title: "Nematode trait data exploration"
author: "Shane Hogle"
date: today
link-citations: true
abstract: "Try and get some general insights into the distribution of different nematode traits"
---

# Code

```{r}
#| eval: true
#| echo: true
#| output: false
#| warnings: false
library(here)
source(here::here("R", "02_ne_trait_exploration.R"))
```

R script with all required code is available at <https://github.com/slhogle/huiyu_projects/blob/main/R/02_ne_trait_exploration.R>

# Plots

::: {#fig-01}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p01
```
X axis: Distribution of nematode volumes ($\mathrm{μm^3}$) after consuming each of the 122 SynCom bacterial species. The x-axis is plotted on a log10 scale. Y axis: the number of observation at each of 20 different volume bins.
:::


::: {#fig-02}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p02
```
X axis: Distribution of nematode dry weights (μg) after consuming each of the 122 SynCom bacterial species. Y axis: the number of observation at each of 20 different weight bins.
:::

::: {#fig-03}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p03
```
X axis: Distribution of nematode dry weights (μg) after consuming each of the 122 SynCom bacterial species. Y axis: the number of observation at each of 20 different weight bins.
:::

::: {#fig-04}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p04
```
X axis: Distribution of nematode feeding preferences of the 122 SynCom species relative to the control bacterial species OP50: $\log_2 \frac{N_{SpX}}{N_{OP50}}$ where $N$ is the count of worms on each species in the foraging assay. Y axis: the number of observations at each of 20 different preference bins.
:::

::: {#fig-05}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p05
```
X axis: Distribution of nematode clearance of the 122 SynCom species relative to the control bacterial species OP50 in liquid, where clearance is measured in OD600 units. Y axis: the number of observations at each of 20 different preference bins.
:::

::: {#fig-06}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p06
```
X axis: Distribution of nematode adult sizes (log2 scale) when feeding on the 122 SynCom species relative to nematode sizes when feeding on the control bacterial species OP50: $\log_2 \frac{V_{SpX}}{V_{OP50}}$ where $V$ is the volume of adult worms ($\mathrm{μm^3}$) when feeding on each bacterial species in the foraging assay. Y axis: the number of observations at each of 20 different preference bins.
:::

::: {#fig-07}
```{r}
#| fig.width: 9
#| fig.height: 4
#| warning: false
#| echo: false
p07
```
X axis: Nematode feeding preferences (log2 scale)of the 122 SynCom species relative to the control bacterial species OP50: $\log_2 \frac{N_{SpX}}{N_{OP50}}$. Y axis: nematode adult sizes (log2 scale) when feeding on the 122 SynCom species relative to nematode sizes when feeding on the control bacterial species OP50: $\log_2 \frac{V_{SpX}}{V_{OP50}}$. Line-ranges of individual points represent 95% confidence intervals estimated for the n=8 assay replicates.
:::
